\mythesistitle

### 2011-12-21 src/synopsis.tex
commented out a package. NBD.
cleaned up library - new sty for thesis files. now Beamer and thesis files can coexist on mylatexlib.sty.

\usepackage{times} 
\usepackage{t1enc}
\usepackage{boxedminipage}
\usepackage{../lib/mylatexlib}

\title{\mythesistitle} 
\author{\myname} 
\date{\MakeUppercase
  {\mysubmissionmonth}} 
\department{\MakeUppercase{\mydept}}

\def \un {\bf 1}
\def \secfirstparatrim {-5mm}
\def \figtabsize {\footnotesize}

% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``{\bf G}irl with Curious Hair''}} 
% \def \BBB {{\em ``{\bf B}rief Interviews with Hideous Men''}}
% \def \TTT {{\em ``Everything and More: A Compact His{\bf T}ory of Infinity''}} 
% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf G}} 
% \def \xBBB {{\bf B}}
% \def \xTTT {{\bf T}}
%%%%%%
% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``Brief {\bf I}nterviews with Hideous Men''}} 
% \def \BBB {{\em ``Broom of the {\bf S}ystem''}}
% \def \TTT {{\em ``Everything and More: {\bf A} Compact History of Infinity''}}
% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf I}} 
% \def \xBBB {{\bf S}}
% \def \xTTT {{\bf A}}
%%%%%%
\def \LLL {{\em ``$\mathbb{B}$rief Interviews with Hideous Men''}}
\def \GGG {{\em ``The String $\mathbb{T}$heory''}} 
\def \BBB {{\em ``[$\mathbb{W}$]Rhetoric and the Math Melodrama''}}
\def \TTT {{\em ``$\mathbb{F}$ate, Time, and Language: An Essay on Free Will''}}
\def \xLLL {\mathbb{B}}
\def \xGGG {\mathbb{T}} 
\def \xBBB {\mathbb{W}}
\def \xTTT {\mathbb{F}}
% {{\em ``{\bf B}rief Interviews with Hideous Men''}} 
% {{\em ``The String {\bf T}heory''}} 
% {{\em ``[{\bf W}]Rhetoric and the Math Melodrama''}}
% {{\em ``{\bf F}ate, Time, and Language: An Essay on Free Will''}}
% {{\em ``Everything and More: A Compact History of In{\bf F}inity''}} 
% {{\em ``Broom of {\bf T}he System''}} 
% {{\em ``Consider the Lobster''}}
% {{\em ``God Bless You, Mr. {\bf F}ranzen''}}
% {{\em ``{\bf L}aughing with Kafka''}} 
% {{\em ``{\bf G}irl with Curious Hair''}} 
% {{\em ``Consider the {\bf L}obster''}}
% {{\em ``{\bf G}od Bless You, Mr. Franzen''}}
% {{\em ``{\bf T}ennis, Trigonometry,
%                                Tornadoes: A Midwestern  Boyhood''}}
% {{\em ``{\bf T}his is Water''}}
% {{\em ``{\bf T}he Pale King''}}

\def \Pa {{\em {\bf Pa}tricia}} 
\def \Pi {{\em {\bf Pi}gpen}}
\def \Sn {{\em {\bf Sn}oopy}}
\def \Wo {{\em {\bf Wo}odstock}}
\def \Vi {{\em {\bf Vi}olet}} 
\def \Li {{\em {\bf Li}nus}} 
\def \Ch {{\em {\bf Ch}arlie}}
\def \Sa {{\em {\bf Sa}lly}}
\def \Fr {{\em {\bf Fr}anklin}} 
\def \Sc {{\em {\bf Sc}hr{\"o}eder}} 
\def \Lu {{\em {\bf Lu}cy}}
\def \xPa {{\bf Pa}} 
\def \xPi {{\bf Pi}} 
\def \xSn {{\bf Sn}}
\def \xWo {{\bf Wo}}
\def \xVi {{\bf Vi}} 
\def \xLi {{\bf Li}} 
\def \xCh {{\bf Ch}}
\def \xSa {{\bf Sa}}
\def \xFr {{\bf Fr}}
\def \xSc {{\bf Sc}} 
\def \xLu {{\bf Lu}}
\def \residenceblock {{\em Infinite Loop}}
\def \WSI {{\em Wallace Studies Institute}}
\def \coneohone {{\em ``Influence of post modernism in Wallace's work''}}
\def \coneohtwo {{\em ``A study on fragmented prose method''}}

@@

%\nocite{*}
\maketitle

@@

A group of students, \Pa, \Pi, \Sn, \Wo, \Vi, \Li, \Ch, \Sa, \Fr,
  \Sc\ and \Lu\ enroll at the
% {\bf Wo}odstock, {\bf Vi}olet, {\bf Li}nus, {\bf Ch}arlie, {\bf
%   Sa}lly, {\bf Re}run, {\bf Sc}hr{\"o}eder} and {\em {\bf Lu}cy}
% enroll at the
  {\WSI} for a liberal arts programme.  As part of their semester
  thesis, they pick a body of work to study and form the namesake
  study groups, {\LLL}, {\GGG}, {\BBB} and {\TTT}\tnote[TH]{put bib
    entries for these works!}. A student will be in at least one study
  group and may be in more than one. For instance, as will be seen
  later, {\Fr} studies both {\LLL} and {\TTT} while \Wo\ studies only
  \BBB.

@@

% \vspace{-3mm}
% \begin{align*}
% U &= \{\xPa,\; \xPi,\; \xSn,\; \xWo,\; \xVi,\; \xLi,\; \xCh,\;
%     \xSa,\; \xFr,\; \xSc,\; \xLu\}\\
% \cF &= \{\xLLL, \xGGG, \xBBB, \xTTT\}\\
% \xLLL &= \{\xCh,\;  \xSa,\;  \xFr,\;  \xSc,\;  \xLu \}\\
% \xGGG &= \{\xPa,\;  \xPi,\;  \xVi,\;  \xCh \}\\
% \xBBB &= \{\xSn,\;  \xPi,\;  \xWo \}\\
% \xTTT &= \{\xVi,\;  \xLi,\;  \xCh,\;  \xFr \}\\
% n &= |U| = 11\\
% m &= |\cF| = 4  
% \end{align*}

@@

% The administration faces a small challenge with their
% accommodation. 
The campus has a residential area {\residenceblock} that has $n$
single occupancy apartments reserved for the study groups'
accommodation.  All these apartments are located such that the streets
connecting them do {\em not} form
loops. Fig~\ref{fig:streetmappathpeople} \tnote[TH]{fig:streetmap}
shows the street map for {\residenceblock}. It may be noted that as a
graph, it classifies as a tree.

\begin{table}[htbp]
  \centering
  {\footnotesize    
    \begin{tabular}{l||l}
      \begin{tabular}{rcl}
        $T $&$=$&$ \text{\em Street map tree of \residenceblock}$\\
        $V(T) $&$=$&$ \{ 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11 \}$\\
        % $\phi^{-1}(V(T)) $&$=$&$ \{ \xSa,\; \xPi,\; \xFr,\; \xWo,\;
        % \xCh,\; \xVi,\;
        % \xPa,\; \xSn,\; \xLu,\; \xLi,\; \xSc \}$\\
        $\cP $&$=$&$ \{R\xLLL, R\xGGG, R\xBBB, R\xTTT\}$\\
        $R\xLLL $&$=$&$ \{9, 1, 5, 3, 11\}$\\
        $R\xGGG $&$=$&$ \{7, 2, 6, 5\}$\\
        $R\xBBB $&$=$&$ \{8, 2, 4 \}$\\
        $R\xTTT $&$=$&$ \{10, 6, 5, 3\}$\\
        $n $&$=$&$ |V| = 11$\\
        $m $&$=$&$ |\cP| = 4$\\\\
        $\cl $&$=$& {\em Study group to route mapping}\\        
        $\cl(\mathbb{X}) $&$=$&  $R\mathbb{X}$ for all $\mathbb{X} \in
        \cF$
      \end{tabular} & 
      \begin{tabular}{c}
       {\em Apartment allocation }($\phi$)\\
                    \begin{tabular}{c|c}                      
                      1  & \xSa\\
                      2  & \xPi\\
                      3  & \xFr\\
                      4  & \xWo\\
                      5  & \xCh\\
                      6  & \xVi\\
                      7  & \xPa\\
                      8  & \xSn\\
                      9  & \xLu\\
                      10 & \xLi\\
                      11 & \xSc                     
                    \end{tabular}
      \end{tabular}\\
    \end{tabular}
  }
  \caption{\figtabsize A solution to study group accommodation problem}
  \label{tab:iltree}
\end{table}

@@

\def \probdefwidth {0.85\linewidth}
\def \FTPL {{\sc Feasible Tree Path Labeling}}
\def \CFTPL {\sc Compute Feasible Path Labeling}

@@

\def \kstar {$k$-subdivided star}
\def \CFTPLKTREE {\sc Compute $k$-subdivided Star Path Labeling}

>>>>

\usepackage{times} 
\usepackage{t1enc}
%\usepackage{boxedminipage}
\usepackage{../lib/mythesislib}
\usepackage{../lib/mylatexlib}

\title{\mythesistitle} 
\author{\myname} 
\date{\MakeUppercase
  {\mysynopsissubmissionmonth}} 
\department{\MakeUppercase{\mydept}}

@@

\maketitle

@@

A group of students, \Pa, \Pi, \Sn, \Wo, \Vi, \Li, \Ch, \Sa, \Fr, \Sc\
and \Lu\ enroll at the {\WSI} for a liberal arts programme.  As part
of their semester thesis, they pick a body of work to study and form
the namesake study groups, {\LLL}, {\GGG}, {\BBB} and
{\TTT}\tnote[TH]{put bib entries for these works!}. A student will be
in at least one study group and may be in more than one. For instance,
as will be seen later, {\Fr} studies both {\LLL} and {\TTT} while \Wo\
studies only \BBB.

@@

@@

The campus has a residential area {\residenceblock} that has $n$
single occupancy apartments reserved for the study groups'
accommodation.  All these apartments are located such that the streets
connecting them do {\em not} form
loops. Fig~\ref{fig:streetmappathpeople} \tnote[TH]{fig:streetmap}
shows the street map for {\residenceblock}. It may be noted that as a
graph, it classifies as a tree.

\begin{table}[htbp]
  \centering
  {\footnotesize    
    \begin{tabular}{l||l}
      \begin{tabular}{rcl}
        $T $&$=$&$ \text{\em Street map tree of \residenceblock}$\\
        $V(T) $&$=$&$ \{ 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11 \}$\\
        $\cP $&$=$&$ \{R\xLLL, R\xGGG, R\xBBB, R\xTTT\}$\\
        $R\xLLL $&$=$&$ \{9, 1, 5, 3, 11\}$\\
        $R\xGGG $&$=$&$ \{7, 2, 6, 5\}$\\
        $R\xBBB $&$=$&$ \{8, 2, 4 \}$\\
        $R\xTTT $&$=$&$ \{10, 6, 5, 3\}$\\
        $n $&$=$&$ |V| = 11$\\
        $m $&$=$&$ |\cP| = 4$\\\\
        $\cl $&$=$& {\em Study group to route mapping}\\        
        $\cl(\mathbb{X}) $&$=$&  $R\mathbb{X}$ for all $\mathbb{X} \in
        \cF$
      \end{tabular} & 
      \begin{tabular}{c}
       {\em Apartment allocation }($\phi$)\\
                    \begin{tabular}{c|c}                      
                      1  & \xSa\\
                      2  & \xPi\\
                      3  & \xFr\\
                      4  & \xWo\\
                      5  & \xCh\\
                      6  & \xVi\\
                      7  & \xPa\\
                      8  & \xSn\\
                      9  & \xLu\\
                      10 & \xLi\\
                      11 & \xSc                     
                    \end{tabular}
      \end{tabular}\\
    \end{tabular}
  }
  \caption{\figtabsize A solution to study group accommodation problem}
  \label{tab:iltree}
\end{table}

@@

@@
